---
title: "Rmarkdown report"
author: "Cyrille Simeu"
date: "`r Sys.Date()`"
output:
  prettydoc::html_pretty:
    theme: architect
    highlight: github
---
```{r, include=FALSE}
require(knitr)
require(DT)
require(kableExtra)
opts_chunk$set(echo= FALSE, comment="", tidy="styler")
```


## Data description
```{r, echo=FALSE}
u<-dim(iris)
```


In this project we consider the classical iris data that can be found in the R **`datasets`** package. This data has _**`r u[2]`**_ columns named **`Sepal.Length`**, **`Sepal.Width`**, **`Petal.Length`**, **`Petal.Width`**, **`Species`** and _**`r u[1]`**_ observations.  
You can find help on these data [here](https://stat.ethz.ch/R-manual/R-devel/library/datasets/html/iris.html)  

## Descriptive analysis

First, we compute some descriptive statistics with the `summary()` function:
```{r}
options(knitr.kable.NA = "")
kable(summary(iris),digits=2, caption = "Descriptive statistics")
```
Second, we use the function **`aggregate`** to get the following table that shows the means of the _**4**_ numerical variables for each species.  
```{r}
dt<-aggregate(. ~Species, data=iris, mean)
kable(dt, digits=2,caption="Means by species")
```

## Linear regression
We use the function **`cor()`** to get the Pearson’s coefficients of correlation between all our numeric variables:
```{r corelation}
dat1<-subset(iris,select = - Species)
kable(cor(dat1),digits=3,caption="Pearson’s coefficients of correlation")
```

Here are _**3**_ scatter plots that show the association between **`Petal.Length`** and the other numerical variables.

```{r plots, fig.align="center",fig.show="hold", fig.cap="Study of iris flowers", out.width="50%"}
plot(iris$Petal.Length, iris$Sepal.Length, xlab="Petal.Length", ylab="Sepal.Length")
plot(iris$Petal.Length, iris$Sepal.Width, xlab="Petal.Length", ylab="Sepal.Width")
plot(iris$Petal.Length, iris$Petal.Width, xlab="Petal.Length", ylab="Petal.Width")
```
Now, we would like to explain the variations in the length of the sepal as a function of the length of the petal. To do so, we use the following linear regression **`lm(Sepal.Length ~ Petal.Length, data = iris)`**. Here is the summary of this model:  
```{r summarystat}
fit<-lm(Sepal.Length ~ Petal.Length, data = iris)
kable(summary(fit)$coef,digits=c(3,3,3,100), caption="Summary of lm: Sepal.Length ~ Petal.Length")
```

The model’s equation is  
```{r}
a<-round(coef(fit)[[2]],3)
b<-round(coef(fit)[[1]],3)
```
$$
\widehat{Sepal.Length}=`r b`+ `r a`Petal.Legth
$$

Here are the data with the regression line:
```{r, fig.cap="The data with the regression line"}
plot(iris$Petal.Length, iris$Sepal.Length, xlab="Petal.Length", ylab="Sepal.Length")
abline(fit)
```

Finally, we use the **`plot(reg)`** command to get some graphical representations of the residuals.
```{r, out.width="50%", fig.show="hold", fig.cap="Residuals of the regression", fig.align="center"}
plot(fit)
```












